### 2015-01-18 src/introduction.Rnw
update intro

% 1. Describe the problem % 2. State your contributions
Mutation analysis is a method for evaluating the quality of test suites. It
involves producing a family of \emph{mutants}, programs with small
differences from the original program, and evaluating the
effectiveness of test suites against these
mutants~\cite{lipton1971fault, ammann2008introduction}. Research by
Andrews et. al~\cite{andrews2005mutation} suggest that mutations can
simulate behavior of real faults.
% thus
% introduced behave in a fashion similar to real faults, with respect to
% the difficulty of detection.

@@

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only a small fraction of randomly selected mutants.
Wong and Mathur found that random sampling fraction as low as 10\%
could provide accurate results~\cite{jia2011analysis}, and was recently
found that it increases at a rate of $O(x^{\frac{1}{4}})$ when program
size increases linearly~\cite{zhang2014empirical}.

@@

Further, quite a few of the influential studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java.

Finally, with bytecode~\footnote{
A \textit{do faster} approach for eliminating
the compilation step to gain execution speed
} based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
, operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

@@

Hence an easy way to evaluate a mutation reduction strategy would be to
see if it promotes such test suites; that is, either test suites with a large
number of non-redundant test cases, or those with a large number of asserts.

>>>>

% 1. Describe the problem % 2. State your contributions
Mutation analysis is a method for evaluating the quality of test suites. It
involves producing a family of \emph{mutants}, programs with small
differences from the original program, and evaluating the
effectiveness of test suites against these
mutants~\cite{lipton1971fault, ammann2008introduction}. Research by
Andrews et. al~\cite{andrews2005mutation,andrews2006using} suggest that
mutations can simulate behavior of real faults. However, mutation analysis
of test suites has not sufficiently permeated software engineering
practice~\cite{daka2014asurvey} even though the need for a tool that is
able to evaluate tests based on their fault finding quality is keenly
felt~\cite{runeson2006asurvey}.

% thus
% introduced behave in a fashion similar to real faults, with respect to
% the difficulty of detection.

@@

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only a small fraction of randomly selected mutants.
Wong and Mathur found that random sampling fraction as low as 10\%
could provide accurate results~\cite{jia2011analysis}. It was recently
found that the fraction required to achieve adequacy on mutation sampling
increases at a rate of $O(x^{\frac{1}{4}})$ when program size increases
linearly~\cite{zhang2014empirical}.

@@

We also note that quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and may not directly applicable to
newer languages such as Java.

Finally, with bytecode~\footnote{
A \textit{do faster} approach for eliminating
the compilation step to gain execution speed
} based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche},
operators based on source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of our approach can be found in
Section~\ref{sec:methodology}.

@@

This suggests that an easy way to evaluate a mutation reduction strategy
would be to see if it promotes such test suites; that is, either test suites
with a large number of non-redundant test cases, or those with a large number
of asserts.
